Modal type theory based on the intuitionistic epistemic logic

### 2018-02-11 article.tex
modifications

  {\bf K} is a monoidal endofunctor
\end{lemma}

@@

Simple, but routine checking.
\end{proof}

>>>>

  {\bf K} is a lax monoidal endofunctor
\end{lemma}

@@

1) Let us define $\tau_{\hat{A} \times \hat{B}, \hat{C}}$ as follows:

$\tau_{\hat{A} \times \hat{B}, \hat{C}} = [p, {\bf \: let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle \langle x,y \rangle, z \rangle]$

Then:

$\begin{array}{lll}
&\text{fmap } \alpha_{\hat{A},\hat{B},\hat{C}} \circ \tau_{\hat{A} \times \hat{B}, \hat{C}} = & \\
&[q, {\bf let \: pure \:} r = q {\: \bf in \:}  \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle] \: \circ & \\
&\quad\quad\quad\quad \circ \: [p, {\bf \: let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle \langle x,y \rangle, z \rangle] = & \\
&[p, {\bf let \: pure \:} r = q {\: \bf in \:}  \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle & \\
&\quad\quad\quad\quad [q := {\bf \: let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle \langle x,y \rangle, z \rangle]] = & \\
&[p, {\bf let \: pure \:} r = ({\bf let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle \langle x,y \rangle, z \rangle) & \\
&\quad\quad\quad\quad {\: \bf in \:} \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle] = & \\
&[p, {\bf let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:}  \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle & \\
&\quad\quad\quad\quad [r := \langle \langle x,y \rangle, z \rangle]] = & \\
&[p, {\bf let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle x, \langle y, z \rangle \rangle]&
\end{array}$

On the other hand:

Let us define as follows $\tau_{\hat{A}, \hat{B} \times \hat{C}}$:

$\begin{array}{lll}
&\tau_{\hat{A}, \hat{B} \times \hat{C}} = [r, {\bf let \: pure \:} x, y, z = ({\bf pure \:} \pi_1 r, {\bf let \: pure \:} q^{'} = \pi_2 r {\: \bf in \:} \pi_1 q^{'}, {\bf let \: pure \:} q^{'} = \pi_2 r {\: \bf in \:} \pi_2 q^{'}) & \\
&\quad\quad\quad\quad {\: \bf in \:} \langle x, \langle y, z \rangle\rangle]& \\
\end{array}$

We may simplify the current instance of tensorial strength:
